The 2014 SMT Competition

### 2015-08-07 2014/report/SMTCOMP.tex
No period (.) at the end of subsection titles (for uniformity).
Layout tweaks to avoid overfull LaTeX boxes.
Table 8 (fraction solved fastest) centered, frames fixed.

\setlength\tabcolsep{3pt}

@@

\subsection{Application benchmarks.}

@@

\subsection{Selection of benchmarks. \label{sec:benchmark-selection}}

@@

\begin{table}[H]
\caption{History of solver participation (numbers in parenthesis indicate
the number of versions submitted for the tool). Complete records of early competitions were not available to the 2014 organizers.}
\label{Table:participants}
\renewcommand{\mark}[0]{\ding{51}}
\centering
\setlength{\tabcolsep}{1pt}
\begin{tabular}{|l@{\,\,}l|c|c|c|c|c|c|c|c|c|}
\hline
Solver & Affiliation & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2014 \\
\hline
4Simp                  & U. Melbourne 	&   &   &   &   &   &   &   &   & \mark  \\
AbzizPortfolio         & U. Cairo       &   &   &   &   &   &   &   & \mark & (2)\\
Alt-Ergo               & U. Paris Sud  &   &   &   & \mark &   &   &   &  &   \\
AProVE NIA             & RWTH Aachen    &   &   &   &   &   & \mark & \mark &   & \mark \\
ArgoLib                &   &   &   & \mark &   &   &   &   &  &   \\
Ario                   &   & \mark & \mark &   &   &   &   &   &  &   \\
barcelogic             & UPC            & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
beaver                 & UC Berkeley   &   &   &   & \mark & \mark &   &   &   &   \\
Boolector              & JKU            &   &   &   & \mark & \mark &   & \mark & \mark & (3)\\
clsat                  & Washington U.  &   &   &   & \mark & \mark &   &   &   &   \\
CVC/CVCLite/CVC3       & NYU, U. Iowa   & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark \\
CVC4	                 & NYU, U. Iowa   &   &   &   &   &   & \mark & \mark & \mark & \mark \\
ExtSat                 &   &   & \mark &   &   &   &   &   &  &   \\
Fx7                    &   &   &   & \mark &   &   &   &   &  &   \\
HTP                    &   & \mark & \mark &   &   &   &   &   &  &   \\
Jat                    &   &   & \mark &   &   &   &   &   &  &   \\
Kleaver	               & Imperial       &   &   &   &   &   &   &   &   & (2) \\
MathSAT 3,4,5          & U. Trento, FBK & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark &   \\
MathSat-HeavyBV        & U. Trento      &   &   &   &   &   &   &   & \mark &   \\
MiniSMT                & U. Innsbruck   &   &   &   &   &   & \mark &   &   &   \\
NuSMV                  & FBK &   & \mark &   &   &   &   &   &  &   \\
OpenSMT, OpenSMT2      & U. Lugano      &   &   &   & \mark & \mark & \mark & \mark &   & \mark \\
raSAT  	               & JAIST          &   &   &   &   &   &   &   &   & \mark \\
Sammy                  &   & \mark &   &   &   &   &   &   &  &   \\
Sateen                 & U. Col-Boulder & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
SBT                    &   & \mark &   &   &   &   &   &   &  &   \\
Simplics               & SRI & \mark &   &   &   &   &   &   &  &   \\
simplifyingSTP         & U. Melbourne   &   &   &   &   &   & \mark &   &   &   \\
SMTInterpol            & U. Freiburg    &   &   &   &   &   &   & \mark & \mark & \mark \\
SONOLAR                & U. Bremen      &   &   &   &   &   & \mark & \mark & \mark & \mark \\
Spear                  &   &   &   & \mark & \mark &   &   &   &  &   \\
STP, STP2              & MIT            &   & \mark &   &   & \mark &   & \mark & \mark &   \\
STP-CryptoMiniSat4     & Security Res. Lab.  &   &   &   &   &   &   &   &   & \mark\\
SVC	               & Stanford U.  & \mark &   &   &   &   &   &   &  &   \\
sword                  & U. Bremen      &   &   &   & \mark & \mark &   &   &   &   \\
test\_pmathsat         & FBK-IRST       &   &   &   &   &   & \mark &   &   &   \\
Tiffany de Wintermonte & U. Melbourne 	&   &   &   &   &   &   &   & \mark &  \\
veriT                  & Loria, UFRN           &   &   &   &   & \mark & \mark & \mark &   & \mark \\
Yices, Yices2          & SRI            & \mark & \mark & \mark & \mark & \mark &   &   &   & \mark \\
Z3                & Microsoft Res.  &   &   & \mark & \mark &   &   & \mark &   &   \\
\hline
Total & & 11 & 11 & 9 & 13 & 12 & 10 & 11 & 11 & 18 \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}
\caption{\label{tab:timeline}Competition timeline}
\scalebox{1}{
\begin{tabular}{r |@{\hspace{-2.3pt}$\bullet$ \hspace{5pt}} p{.8\textwidth}}
Jul. 2013 & Cok appointed as chair of the organizing committee\\
Dec. 2013 & D\'{e}harbe and Weber appointed as co-organizers\\
21 Jan. 2014 & call for applications and benchmarks\\
15 May 2014 & deadline for new benchmarks; benchmarks were being corrected and curated throughout May and June, until the final solver deadline\\
19 May 2014 & revised competition rules posted\\
1 Jun. 2014 & deadline for initial solver registration; final competition rules posted\\
15 Jun. 2014 & deadline for final solver registration\\
16 Jun. 2014 & computation begins\\
22 Jun. 2014 & main track computation ends; official results posted on 27~June\\
22 Jun. 2014 & deadline for application track solvers\\
28 Jun. 2014 & application track computation\\
17 Jul. 2014 & SMT Workshop at which results were announced\\
21 Jul. 2014 & FLoC Olympic Games Awards Ceremony
\end{tabular}
}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|lll|}
\hline
Logic & Fraction solved fastest & \\
\hline
ALIA & 51\% [Z3] & 48\% veriT  & \\
AUFLIA & 66\% [Z3] & 33\% CVC3  & \\
AUFLIRA & 60\% [Z3] & 37\% veriT & 1\% CVC3 \\
AUFNIRA & 72\% [Z3] & 23\% CVC3 & 2\% CVC4 \\
LIA & 43\% CVC4 & 30\% [Z3] & 17\% CVC3 \\
LRA & 42\% CVC4 & 38\% veriT & 18\% [Z3] \\
NIA & 66\% [Z3] & 33\% CVC4  & \\
NRA & 96\% CVC4 & 3\% [Z3]  & \\
QF\_ABV & 78\% Yices2 & 9\% SONOLAR & 7\% Kleaver-STP \\
QF\_ALIA & 95\% Yices2 & 4\% [Z3] & \\
QF\_AUFBV & 81\% Yices2 & 10\% [MathSAT] & 5\% [Z3] \\
QF\_AUFLIA & 60\% Yices2 & 38\% [Z3] & 1\% CVC4 \\
QF\_AX & 92\% Yices2 & 6\% [Z3] & 0\% CVC4 \\
QF\_BV & 33\% Yices2 & 25\% [Z3] & 13\% 4Simp \\
QF\_IDL & 87\% Yices2 & 11\% [Z3] & 0\% veriT \\
QF\_LIA & 76\% Yices2 & 11\% [Z3] & 7\% CVC4 \\
QF\_LRA & 86\% Yices2 & 3\% veriT & 3\% CVC4 \\
QF\_NIA & 90\% [Z3] & 7\% AProVE & 1\% CVC3 \\
QF\_NRA & 88\% [Z3] & 6\% CVC4 & 4\% CVC3 \\
QF\_RDL & 71\% Yices2 & 25\% [Z3] & 3\% veriT \\
QF\_UF & 96\% Yices2 & 1\% veriT & 1\% [Z3] \\
QF\_UFBV & 96\% Yices2 & 3\% [MathSAT]  & \\
QF\_UFIDL & 59\% [Z3] & 36\% Yices2 & 3\% veriT \\
QF\_UFLIA & 97\% Yices2 & 2\% [Z3] & 0\% CVC4 \\
QF\_UFLRA & 91\% Yices2 & 4\% [Z3] & 2\% veriT \\
QF\_UFNIA & 100\% CVC4 & \\
QF\_UFNRA & 59\% CVC3 & 37\% [Z3] & 3\% CVC4 \\
UF & 37\% veriT & 32\% CVC4 & 24\% [Z3] \\
UFIDL & 57\% CVC4 & 42\% [Z3]  & \\
UFLIA & 56\% [Z3] & 35\% veriT & 7\% CVC4 \\
UFLRA & 95\% veriT & 4\% [Z3]  & \\
UFNIA & 80\% [Z3] & 10\% CVC3 & 9\% CVC4 \\

>>>>

\setlength\tabcolsep{2.9pt}

@@

\subsection{Application benchmarks}

@@

\subsection{Selection of benchmarks}
\label{sec:benchmark-selection}

@@

\begin{table}[H]
\caption{History of solver participation (numbers in parenthesis indicate
  the number of versions submitted for the tool). Complete records of early competitions were not available to the 2014 organizers.}
\label{Table:participants}
\renewcommand{\mark}[0]{\ding{51}}
\centering
\setlength{\tabcolsep}{1pt}
\scalebox{1}[.984]{\begin{tabular}{|l@{\,\,}l|c|c|c|c|c|c|c|c|c|}
\hline
Solver & Affiliation & 2005 & 2006 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2014 \\
\hline
4Simp                  & U. Melbourne 	&   &   &   &   &   &   &   &   & \mark  \\
AbzizPortfolio         & U. Cairo       &   &   &   &   &   &   &   & \mark & (2)\\
Alt-Ergo               & U. Paris Sud  &   &   &   & \mark &   &   &   &  &   \\
AProVE NIA             & RWTH Aachen    &   &   &   &   &   & \mark & \mark &   & \mark \\
ArgoLib                &   &   &   & \mark &   &   &   &   &  &   \\
Ario                   &   & \mark & \mark &   &   &   &   &   &  &   \\
barcelogic             & UPC            & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
beaver                 & UC Berkeley   &   &   &   & \mark & \mark &   &   &   &   \\
Boolector              & JKU            &   &   &   & \mark & \mark &   & \mark & \mark & (3)\\
clsat                  & Washington U.  &   &   &   & \mark & \mark &   &   &   &   \\
CVC/CVCLite/CVC3       & NYU, U. Iowa   & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark \\
CVC4	                 & NYU, U. Iowa   &   &   &   &   &   & \mark & \mark & \mark & \mark \\
ExtSat                 &   &   & \mark &   &   &   &   &   &  &   \\
Fx7                    &   &   &   & \mark &   &   &   &   &  &   \\
HTP                    &   & \mark & \mark &   &   &   &   &   &  &   \\
Jat                    &   &   & \mark &   &   &   &   &   &  &   \\
Kleaver	               & Imperial       &   &   &   &   &   &   &   &   & (2) \\
MathSAT 3,4,5          & U. Trento, FBK & \mark & \mark & \mark & \mark & \mark & \mark & \mark & \mark &   \\
MathSat-HeavyBV        & U. Trento      &   &   &   &   &   &   &   & \mark &   \\
MiniSMT                & U. Innsbruck   &   &   &   &   &   & \mark &   &   &   \\
NuSMV                  & FBK &   & \mark &   &   &   &   &   &  &   \\
OpenSMT, OpenSMT2      & U. Lugano      &   &   &   & \mark & \mark & \mark & \mark &   & \mark \\
raSAT  	               & JAIST          &   &   &   &   &   &   &   &   & \mark \\
Sammy                  &   & \mark &   &   &   &   &   &   &  &   \\
Sateen                 & U. Col-Boulder & \mark & \mark & \mark & \mark & \mark &   &   &   &   \\
SBT                    &   & \mark &   &   &   &   &   &   &  &   \\
Simplics               & SRI & \mark &   &   &   &   &   &   &  &   \\
simplifyingSTP         & U. Melbourne   &   &   &   &   &   & \mark &   &   &   \\
SMTInterpol            & U. Freiburg    &   &   &   &   &   &   & \mark & \mark & \mark \\
SONOLAR                & U. Bremen      &   &   &   &   &   & \mark & \mark & \mark & \mark \\
Spear                  &   &   &   & \mark & \mark &   &   &   &  &   \\
STP, STP2              & MIT            &   & \mark &   &   & \mark &   & \mark & \mark &   \\
STP-CryptoMiniSat4     & Security Res. Lab.  &   &   &   &   &   &   &   &   & \mark\\
SVC	               & Stanford U.  & \mark &   &   &   &   &   &   &  &   \\
sword                  & U. Bremen      &   &   &   & \mark & \mark &   &   &   &   \\
test\_pmathsat         & FBK-IRST       &   &   &   &   &   & \mark &   &   &   \\
Tiffany de Wintermonte & U. Melbourne 	&   &   &   &   &   &   &   & \mark &  \\
veriT                  & Loria, UFRN           &   &   &   &   & \mark & \mark & \mark &   & \mark \\
Yices, Yices2          & SRI            & \mark & \mark & \mark & \mark & \mark &   &   &   & \mark \\
Z3                & Microsoft Res.  &   &   & \mark & \mark &   &   & \mark &   &   \\
\hline
Total & & 11 & 11 & 9 & 13 & 12 & 10 & 11 & 11 & 18 \\
\hline
\end{tabular}}
\end{table}

@@

\begin{table}
\caption{\label{tab:timeline}Competition timeline}
\begin{tabular}{r |@{\hspace{-2.3pt}$\bullet$ \hspace{5pt}} p{.75\textwidth}}
Jul. 2013 & Cok appointed as chair of the organizing committee\\
Dec. 2013 & D\'{e}harbe and Weber appointed as co-organizers\\
21 Jan. 2014 & call for applications and benchmarks\\
15 May 2014 & deadline for new benchmarks; benchmarks were being corrected and curated throughout May and June, until the final solver deadline\\
19 May 2014 & revised competition rules posted\\
1 Jun. 2014 & deadline for initial solver registration; final competition rules posted\\
15 Jun. 2014 & deadline for final solver registration\\
16 Jun. 2014 & computation begins\\
22 Jun. 2014 & main track computation ends; official results posted on 27~June\\
22 Jun. 2014 & deadline for application track solvers\\
28 Jun. 2014 & application track computation\\
17 Jul. 2014 & SMT Workshop at which results were announced\\
21 Jul. 2014 & FLoC Olympic Games Awards Ceremony
\end{tabular}
\end{table}

@@

\begin{table}
\centering\begin{tabular}{|l|lll|}
\hline
Logic & Fraction solved fastest & & \\ \hline
ALIA & 51\% [Z3] & 48\% veriT  & \\
AUFLIA & 66\% [Z3] & 33\% CVC3  & \\
AUFLIRA & 60\% [Z3] & 37\% veriT & 1\% CVC3 \\
AUFNIRA & 72\% [Z3] & 23\% CVC3 & 2\% CVC4 \\
LIA & 43\% CVC4 & 30\% [Z3] & 17\% CVC3 \\
LRA & 42\% CVC4 & 38\% veriT & 18\% [Z3] \\
NIA & 66\% [Z3] & 33\% CVC4  & \\
NRA & 96\% CVC4 & 3\% [Z3]  & \\
QF\_ABV & 78\% Yices2 & 9\% SONOLAR & 7\% Kleaver-STP \\
QF\_ALIA & 95\% Yices2 & 4\% [Z3] & \\
QF\_AUFBV & 81\% Yices2 & 10\% [MathSAT] & 5\% [Z3] \\
QF\_AUFLIA & 60\% Yices2 & 38\% [Z3] & 1\% CVC4 \\
QF\_AX & 92\% Yices2 & 6\% [Z3] & 0\% CVC4 \\
QF\_BV & 33\% Yices2 & 25\% [Z3] & 13\% 4Simp \\
QF\_IDL & 87\% Yices2 & 11\% [Z3] & 0\% veriT \\
QF\_LIA & 76\% Yices2 & 11\% [Z3] & 7\% CVC4 \\
QF\_LRA & 86\% Yices2 & 3\% veriT & 3\% CVC4 \\
QF\_NIA & 90\% [Z3] & 7\% AProVE & 1\% CVC3 \\
QF\_NRA & 88\% [Z3] & 6\% CVC4 & 4\% CVC3 \\
QF\_RDL & 71\% Yices2 & 25\% [Z3] & 3\% veriT \\
QF\_UF & 96\% Yices2 & 1\% veriT & 1\% [Z3] \\
QF\_UFBV & 96\% Yices2 & 3\% [MathSAT]  & \\
QF\_UFIDL & 59\% [Z3] & 36\% Yices2 & 3\% veriT \\
QF\_UFLIA & 97\% Yices2 & 2\% [Z3] & 0\% CVC4 \\
QF\_UFLRA & 91\% Yices2 & 4\% [Z3] & 2\% veriT \\
QF\_UFNIA & 100\% CVC4 & & \\
QF\_UFNRA & 59\% CVC3 & 37\% [Z3] & 3\% CVC4 \\
UF & 37\% veriT & 32\% CVC4 & 24\% [Z3] \\
UFIDL & 57\% CVC4 & 42\% [Z3]  & \\
UFLIA & 56\% [Z3] & 35\% veriT & 7\% CVC4 \\
UFLRA & 95\% veriT & 4\% [Z3]  & \\
UFNIA & 80\% [Z3] & 10\% CVC3 & 9\% CVC4 \\
